Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-09 ms.Rnw
Minor aesthetic changes to table
minor adjustments based on model 2 changes

\begin{figure}[ht]
<<Mod2Fit_and_Scenarios_Figure, fig.height=2, fig.width=5, fig.align='center'>>=
ggplot() +
  geom_line(data = h2_traj, aes(x = date, y = Ctotal + 1), col = 'blue') +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(data = filter(mod2_VaccScenarios$all_trajs,
                          year >= max(h2_traj$year)),
            aes(x = as.Date(date), y = ReportedCases + 1, color = scenario)) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 8)) +
  ylab("Reported cholera cases") +
  scale_color_manual(values = c("V0" = '#f4a582',
                                "V1" = '#d6604d',
                                "V2" = '#b2182b',
                                "V3" = '#92c5de',
                                "V4" = '#4393c3')) +
  geom_vline(xintercept = yearsToDate(2014.161), linetype = 'dashed') +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption{\label{fig:mod2Traj}
Simulated trajectory of Model~2 (blue curve) and projections under the various vaccination scenarios.
Reported cholera incidence is shown in black.
The dashed vertical line shows where the endemic phase starts and parameter values are re-estimated.
Note that the various vaccination scenarios had little effect on the projected cholera cases.
This is because the primary effect of vaccines in Model~2 is to remove individuals from the susceptible pool,
yet reported number of cholera infections were low and decreasing at the start of the vaccination campaigns (only $\Sexpr{true_agg_cases$ReportedAll[nrow(true_agg_cases)]}$ cases were reported in all of Haiti),
so this had very little effect on cholera transmission.
}
\end{figure}

@@

  & \missing

@@

  & $\begin{array}{l} \seasAmplitude=\Sexpr{myround(p3s["lambdaR"],2)} \\ r=\Sexpr{myround(p3s["r"],2)} \end{array}$

@@

    \muRS^{-1}= \Sexpr{myround(1/h2_fit$epi_params["sigma"],1)} \\

@@

      \hspace{-1mm} \transmission=(
      \Sexpr{signif(h2_fit$epi_params["Beta"],2)}, \\
      \Sexpr{signif(h2_fit$end_params["Beta"],2)}
      )\end{array}$

@@

    \beta_W= (\Sexpr{signif(h2_fit$epi_params["BetaW"],3)}, \Sexpr{signif(h2_fit$end_params["BetaW"],3)})

@@

      \hspace{-1mm} \Wshed = (
      \Sexpr{signif(h2_fit$epi_params["Mu"],3)}, \\
      \Sexpr{signif(h2_fit$end_params["Mu"],3)}

@@

      \hspace{-1mm} \Wremoval^{-1} = (
      \Sexpr{signif(52/h2_fit$epi_params["Delta"],3)}, \\
      \Sexpr{signif(52/h2_fit$end_params["Delta"],1)}

>>>>

\begin{figure}[ht]
<<Mod2Fit_and_Scenarios_Figure, fig.height=2, fig.width=5, fig.align='center'>>=
ggplot() +
  geom_line(data = h2_traj, aes(x = date, y = Ctotal + 1), col = 'blue') +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(data = filter(mod2_VaccScenarios$all_trajs,
                          year >= max(h2_traj$year)),
            aes(x = as.Date(date), y = ReportedCases + 1, color = scenario)) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 8)) +
  ylab("Reported cholera cases") +
  scale_color_manual(values = c("V0" = '#f4a582',
                                "V1" = '#d6604d',
                                "V2" = '#b2182b',
                                "V3" = '#92c5de',
                                "V4" = '#4393c3')) +
  # geom_vline(xintercept = yearsToDate(2014.161), linetype = 'dashed') +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption{\label{fig:mod2Traj}
Simulated trajectory of Model~2 (blue curve) and projections under the various vaccination scenarios.
Reported cholera incidence is shown in black.}
\end{figure}

@@

  & \multicolumn{1}{c}{\hspace{16pt}\missing}

@@

  & $\begin{array}{l} \seasAmplitude=\Sexpr{myround(p3s["lambdaR"],2)} \\ r=\Sexpr{signif(p3s["r"],3)} \end{array}$

@@

    \muRS^{-1}= \Sexpr{signif(1/h2_fit$epi_params["sigma"],2)} \\

@@

  & $\transmission=$\Sexpr{signif(h2_fit$epi_params["Beta"],3)}

@@

    \beta_W= \Sexpr{signif(h2_fit$epi_params["BetaW"],3)}

@@

  & $\Wshed = $ \Sexpr{signif(h2_fit$epi_params["Mu"],3)}

@@

  & $\Wremoval^{-1} = $ \Sexpr{signif(52/h2_fit$epi_params["Delta"],3)}
